Ornaments as indicators of social changes resulting from indirect effects of colonialism in northeastern Taiwan

### 2020-09-21 analysis/paper/paper.Rmd
udpate C14 calibration method

                               # Use Bchron to clibrate
library(Bchron)

kw_dates_with_error_calibrated <- 
  with(kw_dates_with_error,
       BchronCalibrate(
         ages = rce,
         ageSds = se,
         ids = id,
         calCurves = rep('intcal13',
                         length(kw_dates_with_error$rce))))

@@

# we can combine all the calibrated dates into a single plot, like this
kw_ages_densities <- 
  with(kw_dates_with_error,
       rrtools:::quietly( # suppress the progress bar
         BchronDensity(
         ages = rce,
         ageSds = se,
         calCurves = rep('intcal13',
                         length(kw_dates_with_error$rce)),
         store_density=TRUE)))

@@

lines_for_periods <- 
  tibble(bx = c(324,  # start of Euro contact, 1626 AD
               182),  # start of Chinese contact, 1768 AD
          by = c(0, 0),
          byend = c(0.0020),
          bxend = bx)

kwl_ages_curve <-
ggplot() +
    geom_area(data = kw_ages_densities_dfs,
            aes(ageGrid,
                dens_to_one,
                group = date),
            fill = "grey80",
            alpha = 0.4,
            position = 'identity') +
    geom_line(data = kw_ages_densities_df,
            aes(ageGrid,
                densities)) +
    geom_segment(data = lines_for_periods,
              aes(x = bx, 
                  y = by, 
                  xend = bxend, 
                  yend = byend),
              colour = c("red", "blue")) +
    annotate("rect", xmin = 100, xmax = 600, 
                   ymin = 0, ymax = lines_for_periods$byend[1],
           fill = "grey80",
           alpha = 0.3) +
    annotate("text", x = 350, y = 0.0026,
           label = "Upper component",
           size = 2) +
    annotate("rect", xmin = 1300, xmax = 800,
                   ymin = 0, ymax = lines_for_periods$byend[1],
           fill = "grey80",
           alpha = 0.3) +
    annotate("text", x = 1050, y = 0.0026,
           label = "Lower component",
           size = 2)  +
  theme_minimal(base_size = 8) +
  xlab("calibrated years BP") +
  ylab("Density") +
  coord_fixed(ratio = 400000)

>>>>

                               # Use Bchron to calibrate
library(Bchron)

kw_dates_with_error_calibrated <- 
  with(kw_dates_with_error,
       BchronCalibrate(
         ages = rce,
         ageSds = se,
         ids = id,
         calCurves = rep('intcal20',
                         length(kw_dates_with_error$rce))))

@@

# we can combine all the calibrated dates into a single plot, like this
kw_ages_densities <- 
  with(kw_dates_with_error,
       rrtools:::quietly( # suppress the progress bar
         BchronDensity(
         ages = rce,
         ageSds = se,
         calCurves = rep('intcal20',
                         length(kw_dates_with_error$rce)),
         store_density=TRUE)))

@@

lines_for_periods <- 
  tibble(bx = c(324,  # start of Euro contact, 1626 AD
               182),  # start of Chinese contact, 1768 AD
          by = c(0, 0),
          byend = c(0.002),
          bxend = bx)

kwl_ages_curve <-
ggplot() +
    geom_area(data = kw_ages_densities_dfs,
            aes(ageGrid,
                dens_to_one,
                group = date),
            fill = "grey80",
            alpha = 0.4,
            position = 'identity') +
    geom_line(data = kw_ages_densities_df,
            aes(ageGrid,
                densities)) +
    geom_segment(data = lines_for_periods,
              aes(x = bx, 
                  y = by, 
                  xend = bxend, 
                  yend = byend),
              colour = c("red", "blue")) +
    annotate("rect", xmin = 100, xmax = 600, 
                   ymin = 0, ymax = lines_for_periods$byend[1],
           fill = "grey80",
           alpha = 0.3) +
    annotate("text", x = 350, y = 0.0026,
           label = "Upper component",
           size = 2.5) +
    annotate("rect", xmin = 1300, xmax = 800,
                   ymin = 0, ymax = lines_for_periods$byend[1],
           fill = "grey80",
           alpha = 0.3) +
    annotate("text", x = 1050, y = 0.0026,
           label = "Lower component",
           size = 2.5)  +
  theme_minimal(base_size = 8) +
  xlab("calibrated years BP") +
  ylab("Density") +
  coord_fixed(ratio = 400000)
